---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fingermatchR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/forensic-science/fingermatchR/workflows/R-CMD-check/badge.svg)](https://github.com/forensic-science/fingermatchR/actions)
<!-- badges: end -->

**FingermatchR** provides fingerprint matching tools based on NIST's MINDTCT and BOZORTH3 algorithms, as released in [NIST's Biometrics Image Software suite (NBIS)](https://www.nist.gov/services-resources/software/nist-biometric-image-software-nbis).

## Installation

Make sure you have NBIS installed with binaries available in PATH. Check in particular that you have the `mindtct` and `bozorth3` executables installed and available:
```bash
$ mindtct -version && bozorth3 -version
Standard Version: ANSI/NIST-ITL 1-2007
NBIS Non-Export Control Software Version: Release 5.0.0
...
```

You can install the development version of **fingermatchR** from [GitHub](https://github.com/) with:

```{r}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("forensic-science/fingermatchR")
```

## Examples

```{r message=FALSE}
library(fingermatchR)
library(dplyr)
```

Optionally, define location of NBIS executables:

```{r}
# This is required if NBIS executables are not available in PATH.
options(NBIS_bin = "/home/olivier/Desktop/Research/forensic-science/NBIS/src/bin")
```

### Minutiae detection

Detect minutiae using mindtct:

```{r}
imgfiles = list.files("data-raw", pattern = "*.png", full.names = TRUE)

# Raw mindtct output
out = mindtct(imgfiles, outputdir="data-raw")

# Tidy minutiae descriptions
minutiae = tidyMinutiae(out)
```

Plot fingerprint image and its binarization with detected minutiae:

```{r}
# Plain and rolled index fingerprints for the same individual
plotMinutiae(out[c(1,3), ])
```

Compute pairwise fingerprint match scores:

```{r}
matchscores(out, outputdir = "data-raw")
```

Compute all-to-all fingerprint match scores between two lists:

```{r}
matchscores(out, out, outputdir = "data-raw")
```

## References

- Watson et al. (2007) [User's Guide to Export ControlledDistribution of NIST Biometric Image Software (NBIS-EC)](https://nvlpubs.nist.gov/nistpubs/Legacy/IR/nistir7391.pdf). National Institute of Standards and Technology.
- Watson et al. (2007) [User's Guide to NIST Biometric Image Software (NBIS)](https://nvlpubs.nist.gov/nistpubs/Legacy/IR/nistir7392.pdf). National Institute of Standards and Technology.
